Computer Science House Constitution

### 2024-04-28 constitution.tex
Revert Leave of Absence (#228)
* Add Leave of Absence back in

* Remove E-Board leave of absence loophole

\asection{Leave of Absence}
A Leave of Absence offers the option for members to take extended time away from their responsibilities to CSH for any number of personal issues including, but not limited to, physical illness, mental illness, or caregiving for a sick family member.
In order to request a Leave of Absence, a member must follow the RIT policy for Leave of Absence located at \url{https://www.rit.edu/policies/d021}.
Additionally, the member should notify the Evals Director of their Leave of Absence, at which point they become exempt from all CSH requirements until they return.

>>>>

\asection{Leave of Absence}
A leave of absence offers the option for members to take extended time away from their responsibilities to House for any number of personal issues including, but not limited to, physical illness, mental illness, or care giving for a sick family member.
CSH recognizes the need for its members to take care of their personal well-being and will support them through the process of requesting a leave of absence.
House will also help reacclimate any returning member back to the culture of House upon their return.
Upon approval of a leave of absence request, the Evals Director is notified and the member's leave is applied immediately.
A member is also allowed to be physically present and also be on a leave of absence.

\asubsection{Leave of Absence Request}
A leave of absence request must include the following information about the member: name, email, phone number, start date, expected return date, and a reason for the leave.
The request is then given to a staff member of ResLife, excluding student employees, for approval.
A leave of absence start date can be backdated.
At no point does E-Board need to be informed of any details relating to the reason for the leave.

\asubsection{Leave of Absence Duration}
A leave of absence can be granted for up to the length of one semester.

\asubsection{Leave of Absence Extension}
A leave of absence can be extended by submitting a new request.

\asubsection{Leave of Absence Return}
A member may return from a leave of absence whichever they choose to.
When a member wishes to return, they must in writing notify a staff member of ResLife, excluding student employees, to end their leave of absence.

\asubsection{Modified Evaluations}
A member may request their evaluation period to be extended by the duration of the leave or to end of the Standard Operating Session, whichever comes first.

\asubsection{Leave of Absence for Executive Board Member}
The duties and responsibilities of an E-Board member on leave are assumed using the process defined in \ref{Appointment of an Interim Director} until the member returns from their leave.
If the member returns before the end of the Standard Operation Session in which they started their leave, they may assume their position and the interim director is removed. % someone gets their position back if they come back during the year for which they were elected
If any point the member's leave is determined by E-Board to be detrimental to be operations of House, any E-Board member may propose an E-Board Vote to require a resignation from the member.
